\documentclass{llncs}

\begin{document}

\begin{thebibliography}{10}

\bibitem{Cousot:Cousot:77}
P.~Cousot and R.~Cousot.
\newblock Abstract interpretation: a unified framework for static analysis of
  programs by construction or approximation of fixpoints.
\newblock In {\em Proc.~POPL'77}, pages 238--252. The ACM Press, 1977.

\bibitem{Cousot:Cousot:79}
P.~Cousot and R.~Cousot.
\newblock Systematic design of program analysis frameworks.
\newblock In {\em Proceedings of the sixth annual ACM symposium on Principles
  of programming languages}, pages 269--282. The ACM Press, 1979.

\bibitem{Cousot:JLP92}
P.~Cousot and R.~Cousot.
\newblock Abstract interpretation and application to logic programs.
\newblock {\em Journal of Logic Programming}, 13(1, 2, 3 and 4):103--179, 1992.

\bibitem{GR96scp}
R.~Giacobazzi and F.~Ranzato.
\newblock Optimal domains for disjunctive abstract interpretation.
\newblock {\em Science of Computer Programming}, 32(1-3):177--210, 1998.

\bibitem{GiacobazziS98}
R.~Giacobazzi and F.~Scozzari.
\newblock A logical model for relational abstract domains.
\newblock {\em ACM Transactions on Programming Languages and Systems},
  20(5):1067--1109, 1998.

\bibitem{Bruynooghe91}
M.~Bruynooghe.
\newblock A practical framework for the abstract interpretation of logic
  progams.
\newblock {\em Journal of Logic Programming}, 10(2):91--124, 1991.

\bibitem{KanamoriJLP93}
T.~Kanamori and T.~Kawamura.
\newblock Abstract interpretation based on {OLDT} resolution.
\newblock {\em Journal of Logic Programming}, 15(1 \& 2):1--30, 1993.

\bibitem{Marriott:JLP92}
K.~Marriott and H.~S{\o}ndergaard.
\newblock Bottom-up dataflow analysis of normal logic programs.
\newblock {\em Journal of Logic Programming}, 13(1--4):181--204, 1992.

\bibitem{Nilsson:88}
U.~Nilsson.
\newblock Towards a framework for abstract interpretation of logic programs.
\newblock In P.~Deransart, B.~Lorho, and J.~Ma{\l}uszynski, editors, {\em
  Proceedings of the First International Workshop on Programming Language
  Implementation and Logic Programming}, volume 348 of {\em Lecture Notes in
  Computer Science}, pages 68--82. Springer, 1988.



\bibitem{Debray89a}
S.K. Debray.
\newblock Static inference of modes and data dependencies in logic programs.
\newblock {\em ACM Transactions on Programming Languages and Systems},
  11(3):418--450, 1989.

\bibitem{Jacobs:JLP92}
D.~Jacobs and A.~Langen.
\newblock Static analysis of logic programs for independent and parallelism.
\newblock {\em Journal of Logic Programming}, 13(1--4):291--314, 1992.

\bibitem{Muthukumar:JLP92}
K.~Muthukumar and M.~Hermenegildo.
\newblock Compile-time derivation of variable dependency using abstract
  interpretation.
\newblock {\em Journal of Logic Programming}, 13(1--4):315--347, 1992.


\bibitem{Janssens:JLP92}
G.~Janssens and M.~Bruynooghe.
\newblock Deriving descriptions of possible values of program variables by
  means of abstract interpretation.
\newblock {\em Journal of Logic Programming}, 13(1--4):205--258, 1992.

\bibitem{Mar-Son:loplas93}
K.~Marriott and H.~S{\o}ndergaard.
\newblock Precise and efficient groundness analysis for logic programs.
\newblock {\em ACM Letters on Programming Languages and Systems},
  2(1--4):181--196, 1993.

\bibitem{Sondergaard:86}
H.~S{\o}ndergaard.
\newblock An application of abstract interpretation of logic programs: occur
  check problem.
\newblock In B.~Robinet and R.~Wilhelm, editors, {\em ESOP 86, European
  Symposium on Programming}, volume 213 of {\em Lecture Notes in Computer
  Science}, pages 324--338. Springer, 1986.

\bibitem{KingL01}
A.~King and L.~Lu.
\newblock A backward analysis for constraint logic programs.
\newblock {\em Theory and Practice of Logic Programming}, 2(4\&5):517--547,
  2002.
\newblock http://xxx.lanl.gov/abs/cs.PL/0201011.


\end{thebibliography}

\end{document}